HAMdetector: A Bayesian regression model that integrates information to detect HLA-associated mutations

### 2021-02-16 docs/main.tex
add possible references for experimentally studying HLA escape

There are several experimental methods available to study HLA escape~\citep{Timm2004}.  \hl{DaHo: use key references, e.g. those that have introduced a technique; alternatively: cite review like articles that give an overview of several experimental methods} However, these methods are relatively slow and costly, especially for screening purposes. A promising approach that makes efficient use of frequently available data is to combine viral genome sequencing, host HLA determination, computational identification by statistical association analysis, and targeted experimental validation~\citep{Carlson2012}.

>>>>

There are several experimental methods available to study HLA escape~\citep{Timm2004}.  \hl{DaHo: use key references, e.g. those that have introduced a technique; alternatively: cite review like articles that give an overview of several experimental methods} \hl{DaHa: see .tex comments for possible citations} However, these methods are relatively slow and costly, especially for screening purposes. A promising approach that makes efficient use of frequently available data is to combine viral genome sequencing, host HLA determination, computational identification by statistical association analysis, and targeted experimental validation~\citep{Carlson2012}.

% IFN-gamma ELISPOT:
% A  Solid-Phase Enzyme-Linked Immunospot (ELISPOT) Assay for Enumeration of Specific Antibody-Secreting Cells \citep{Czerkinsky1983}
% Quantification of antigen specific CD8+ T cells using an ELISPOT assay \citep{Miyahira1995}

% Chromium release
% Quantitative assay of the lytic action of immune lymphoid cells on 51-Cr-labelled allogeneic target cells in vitro; inhibition by isoantibody and by drugs \citep{Brunner1968}

% Intracellular cytokine staining
% Intracellular cytokine optimization and standard operating procedure \citep{Lamoreaux2006}
% The assessment of antigen-specific CD8+ T cells through the combination of MHC class I tetramer and intracellular staining \citep{Appay2002}

% HLA tetramer staining
% Phenotypic analysis of antigen-specific T lymphocytes \citep{Altman1996}
